---
title: "Part A: Modeling the Medical Jurisprudence Documents"
author: "Nettles"
date: "November 20, 2016"
output:
  html_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Outline:
Intro:
- discussion of non-binary understanding of whitness in real practice; racial ordering; theoretical construct of racial ordering (the framework I will attempt to recreate)
- description of data source
Part A: creation of racial taxonomies
Part B: measurement of racial identity
Part C: chronological measurement to test assertions about fluidity
Part D: reapplicability testing against second corpus 
  
<p><b>Part A: Building a Taxonomy of Racial Terms:</b></p>
<p>The corpus for this trial is a set of 123 medical jurisprudence texts extracted from the MoML. These .txt files were read in R and processed using the wordVectors package to create a word embedded model (WEM). [FN - Schmidt] Word embedded models measure spatial relationships between words, which enables examination of these relationships on the basis of their nearness (similarity) or distance (less similarity.)</p>
<p>An advantage of a WEM is that the analyst does not have to rely on a trial and error process of keyword searches to identify a set of related terms. Keyword searches are at risk of being incomplete, inaccurate because of changes in usage, or biases by contemporary sensibilities. In the WEM, the terms are suggested by spatial relationships between the words themselves.By iteratively modeling terms "nearest_to" a set of general "seed" labels ("race", "races", "racial"), an inclusive list of overall racial terms was created. This set was used to build the seed terms for individual racial groups and further modeling. As new terms were identified for a specific group, they were added back into the overall racial terms list. </p>

<p>The modeling process required some decisions about inclusion of certain types of words. When modeling racial terms, the model quickly begins to include religion and geographic locations. For example, "Jew" refers to both race and religion; I included it in the list because the Jewish people are often treated as a race during this period. More generic terms, such as "ethnic" are included because they typically refer to people viewed as "other." Geographic terms were excluded if they could not also apply to a group of people, i.e., "germany" was excuded, "germanic" was included.</p>

Once the term sets were identified, they were modeled to identify the 150 words closest to that vector set.


```{r libraries, include=FALSE}
#Kim's base library
#library(textmineR)
library(dplyr)
#library(lubridate)
#library(stringr)
#library(tokenizers)
#library(text2vec)
#library(readr)
library(Matrix)
#library(broom)
#library(tidyr)
#library(ggplot2)
library(wordVectors)
library(tsne)
library(stringr)
library(tibble)


```

```{r read in vectors to model, include=FALSE}
model = read.vectors("C:/Users/Kim/Documents/Text Analysis for Historians/moml/mjp_doc_vectors.bin")

```
The collective list of racial terms for medical jurisprudence are:
```{r model for all races, include=FALSE}
all_race_terms <- c("race", "races" , "racial" ,
"ethnic" , "caucasian" , "esquimaux","australoid" ,  "australians", "negroid" , "mongolians" , "aboriginal","european" , "europeans" , "eskimo" , "mongolian" , "malays" , "mohammedans" , "chaldaic" , "mulattoes" , "negro" , "negress" , "japanese" , "african" , "italians" , "africans" , "jews", "tribes" , "hottentots" , "asiatics",   "mexican" , "chaco" , "hebrew" , "chinese" , "islanders" , "hindoos" , "germanic" , "scandinavian" , "arab" , "egyptian" , "persian" , "greeks" , "saxons", "indians", "anglo" , "canaanites" , "norweigan" , "peruvian" , "peruvians" , "oriental" , "georgian" , "scandinavian" , "creole", "jewish", "georgian" , "scandinavian", "roman", "romans" ,  "carthagenians", "swedes", "grecians")

some_races = model %>%
  nearest_to(model[[all_race_terms]],150) %>% names
saveRDS(some_races, "some_races.RDS")

races_all = nearest_to(model,model[[ all_race_terms ]],150)
```

```{r, echo=FALSE}
list(all_race_terms)
```
<p>Next, I created models of terms for specific racial groups so that they can be compared. Bearing in mind that these term sets are a reflection of what the texts themselves have to say about racial relationships, it is worth taking a look at the results. </p>
<p> "Whiteness" appears to be determined more by why it <i>is not</i> than by what it <i>is</i>. Twenty-two terms define Asians, including references to Jews, Muslims, and Hindus. Twelve terms define "blackness." "Whiteness," on the other hand, is defined by just four terms. Europeans are defined by their points of origin; a more precise rendering of them as a racial category would probably include a division between southern and eastern Europeans versus anglo-saxon countries.</p>

<p>The nomenclature "blackness" was chosen over "African American" because the included terms did not necessarily refer to U.S. citizens. Of the available choices, "black" aligns with the terms used by other texts on the subject.



```{r creating the Asian variable, include=FALSE}
asian_terms <- c( "esquimaux","australoid" ,  "australians", "mongolians" , "aboriginal","eskimo" , "anthropoid" ,  "australians" , "mongolian" , "malays" , "mohammedans" , "chaldaic" , "japanese" , "jews", "tribes" , "asiatics", "hebrew" , "chinese" , "islanders" , "hindoos" , "indians", "oriental")

races_asian = nearest_to(model,model[[ asian_terms ]],150)

```


```{r creating afram variable, include=FALSE}

black_terms <- c("negroid" , "mulattoes" , "breeds" ,  "negro" , "negress" , "negroid" ,"african" ,  "africans" , "hottentots" , "creole" , "mongolians" )

races_black = nearest_to(model,model[[black_terms]],150)

```

```{r creating white variable, include=FALSE}
white_terms <- c("caucasian",  "germanic" , "scandinavian" , "saxons", "anglo")

races_white = nearest_to(model,model[[white_terms]],150)

```

```{r creating hispanic variable, include=FALSE}
hispanic_terms <-c("mexican" , "aboriginal" , "chaco" , "peruvian" , "peruvians" , "indians" , "spanish")

races_hispanic = nearest_to(model,model[[hispanic_terms]],150)
```

```{r creating european variable, include=FALSE}
european_terms<- c("european" , "europeans" , "italians" ,  "germanic" , "scandinavian" ,  "greeks" , "saxons",  "anglo" ,  "norweigan" , "georgian" , "scandinavian", "roman", "romans" ,  "carthagenians", "swedes", "grecians")

races_european = nearest_to(model,model[[european_terms]],150)
```
Asian terms: 
```{r, echo=FALSE}
list(asian_terms)
```


African American terms:
```{r, echo=FALSE}
list(black_terms)
```

European terms:
```{r, echo=FALSE}
list(european_terms)
```
Hispanic terms:
```{r, echo=FALSE}
list(hispanic_terms)
```
White terms:
```{r, echo=FALSE}
list(white_terms)

```

```{r, creating jewish variable, include=FALSE}
jewish_terms <- c("jews", "tribes" , "hebrew" ,"jewish", "chaldaic")
races_jewish = nearest_to(model,model[[jewish_terms]],300)
```
Jewish terms:
```{r, echo=FALSE}
list(jewish_terms)
```

<p>Where are the Irish?</>
<p>The term "irish" did not arise during any of the modeling.  This is surprising, given their large scale immigration to the United States during this period and their history as "less white" than other groups.  A model of the term explains why: "irish" appears in the texts, but not in significant relation to other racial terms.
```{r looking for the Irish}
irish_terms <- c("irish"  )

races_irish = nearest_to(model,model[[irish_terms]],150)

head(races_irish, 20)

```
In a similar vein, Native Americans do not appear in the texts. Modeling of "indian" and "tribes" indicates that the relationships refer to India and Asian topics. The names of selected Native American tribes yielded null values.

<p><b>Measuring Whiteness</b></p>
<p>Having established the terms used within the text to define racial identities, the next step is to examine the assertion that while race may be binary in theory, in practice it operates along a continuum. (several examples of this; do comparisons illustrate position change based upon which groups are being compared?  Instead of a linear relationship, identity triangulates in realtion to all others.  Move on to Kim's depiction and then do the meat/veg example.)

```{r Cosine Similarity Scores, echo=FALSE}
#1. Create races model
races = model[rownames(model) %in% some_races [1:75], ]
#2. African American Cosine Similarity Score
black_score = races %>% cosineSimilarity(model[[names(races_black)]])
#3. Asian Cosine Similarity Score
asian_score = races %>% cosineSimilarity(model[[names(races_asian)]])
#4. Caucasian Cosine Similarity Score
caucasian_score = races %>% cosineSimilarity(model[[names(races_white)]])
#5. Hispanic Cosine Similarity Score
hispanic_score = races %>% cosineSimilarity(model[[names(races_hispanic)]])
#6. European Cosine Similarity Score
european_score = races %>% cosineSimilarity(model[[names(races_european)]])
#7. Jewish Cosine Similarity Score
jewish_score = races %>% cosineSimilarity(model[[names(races_jewish)]])
#8. Christian Cosine Similarity Score
#christian_score = races %>% cosineSimilarity(model[[names(races_christian)]])
#9. Muslim Cosine Similarity Score
#muslim_score = races %>% cosineSimilarity(model[[names(races_muslim)]])
#10. All races
all_races_score = races %>% cosineSimilarity(model[[names(races_all)]])
#11. Insider Cosine Similarity Score
#insider_score = races %>% cosineSimilarity(model[[names(races_insider)]])
#12. Outsider Cosine Similarity Score
#outsider_score = races %>% cosineSimilarity(model[[names(races_outsider)]])

```

```{R Plotting Cosine Similarities, include=TRUE}

#1. White vs Black
png(filename="black_vs_white_cosineimilarities.png")
plot(black_score, caucasian_score, type ='n', main="Top 150 words plotted by their similarity to Black\n(x axis) and White (y axis).")
text(black_score, caucasian_score, labels = rownames(races), cex=.7)
abline(a=0, b=1)
dev.off()


#2.Asian vs Black 
png(filename="asian_vs_black_cosineimilarities.png")
plot(black_score, asian_score, type ='n', main="Top 150 words plotted by their similarity to AA\n(x axis) and Asians (y axis).")
text(black_score, asian_score, labels = rownames(races), cex=.7)
abline(a=0, b=1)
dev.off()

#3. Caucasian vs Asian
plot(asian_score, caucasian_score, type ='n', main="Top 150 words plotted by their similarity to Asian\n(x axis) and Caucasians (y axis).")
text(asian_score, caucasian_score, labels = rownames(races), cex=.7)
abline(a=0, b=1)

#4. Caucasian vs Jewish
plot(jewish_score, caucasian_score, type ='n', main="Top 150 words plotted by their similarity to Jewish\n(x axis) and Caucasians (y axis).")
text(jewish_score, caucasian_score, labels = rownames(races), cex=.7)
abline(a=0, b=1)

#5. All Races vs Caucasian
plot(all_races_score, caucasian_score, type ='n', main="Top 150 words plotted by their similarity to All Races\n(x axis) and Caucasians (y axis).")
text(all_races_score, caucasian_score, labels = rownames(races), cex=.7)
abline(a=0, b=1)


#6. Caucasian vs European
plot(european_score, caucasian_score, type ='n', main="Top 150 words plotted by their similarity to european\n(x axis) and Caucasians (y axis).")
text(all_races_score, caucasian_score, labels = rownames(races), cex=.7)
abline(a=0, b=1)



```
This is a comparison of the four racial groups in terms of their nearness to one another:
```{r creating comparative vectors, include=FALSE}

all_races = data.frame(word = rownames(races))

#White vs black vector
white_black_vector = model[[(names(races_white))]] - model[[(names(races_black))]]
all_races$white_vs_black = cosineSimilarity(races, white_black_vector)

#european vs asian vector
european_asian_vector = model[[(names(races_european))]] - model[[(names(races_asian))]]
all_races$european_vs_asian = cosineSimilarity(races, european_asian_vector)

#hispanic vs asian vector
hispanic_asian_vector = model[[(names(races_hispanic))]] - model[[(names(races_asian))]]
all_races$hispanic_vs_asian = cosineSimilarity(races, hispanic_asian_vector)


#black vs asian vector
black_asian_vector = model[[(names (races_black))]] - model[[(names (races_asian))]]
all_races$black_vs_asian = cosineSimilarity(races,black_asian_vector)

#asian vs black vector
asian_black_vector = model[[(names (races_asian))]] - model[[(names (races_black))]]
all_races$asian_vs_black = cosineSimilarity(races,asian_black_vector)

#white vs hispanic vector
white_hispanic_vector = model[[(names(races_white))]] - model[[(names(races_hispanic))]]
all_races$white_vs_hispanic = cosineSimilarity(races, white_hispanic_vector)

#white vs jewish vector
white_jewish_vector = model[[(names (races_jewish))]] - model[[(names (races_white))]]
all_races$white_vs_jewish = cosineSimilarity(races, white_jewish_vector)

#insider vs outside take 2
inside_outside_vector = model[[(names(races_white))]] - model[[(names(races_all))]]
all_races$inside_vs_outside = cosineSimilarity(races, inside_outside_vector)
```

```{r plotting racial fields black/white and inside/outside, echo=FALSE}

library(ggplot2)


ggplot(all_races,aes(x=inside_vs_outside,y=white_vs_black,label=word)) + geom_text(size=2.5) +
  scale_y_continuous("<----- Black ..............  White ------>",limits=c(-.5,.5)) +
  scale_x_continuous("<----- Outside ..............  Inside ------>",limits=c(-.55,.45))

ggsave("mjp_race_scales.jpg")
```


